Kindly Bent to Free Us

### 2019-11-20 kindly/motivation.tex
Fix unsound typos.

\begin{lstlisting}
val fold :
  ('b:'k),('k <= aff_r) =>
  (&(aff_r1,'a) -> 'b -{aff_r1}> 'b) -> &('a array) -> 'b -{lin}> 'b
\end{lstlisting}

@@

\begin{lstlisting}
val iter_mut : &!('a array) -> (&!(aff_r1,'a) -{un_r1}> unit) -{lin}> unit
\end{lstlisting}

Here, the callback of the @iter@ function must be of kind @un_r1@: Indeed, this
callback should be @un@, as it will be called multiple time, but it should also
be prevented from capturing objects of the region $r+1$ to prevent the borrow
from escaping.

>>>>

\begin{lstlisting}
val fold :
  ('b:'k),('k <= aff_r) =>
  (&(aff_r1,'a) -> 'b -{aff_r}> 'b) -> &('a array) -> 'b -{lin}> 'b
\end{lstlisting}

@@

\begin{lstlisting}
val iter_mut : &!('a array) -> (&!(aff_r1,'a) -{un_r}> unit) -{lin}> unit
\end{lstlisting}

Here, the callback of the @iter@ function must be of kind @un_r@: Indeed, this
callback should be @un@, as it will be called multiple time, but it should also
be prevented from capturing objects of the region $r+1$ to prevent the borrow
from escaping.
